---
title: "Alcohol vs Seat choice"
author: "mariah"
date: "summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
# Introduction
Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

The data came from UcDavis in the year...

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.   

# Methods
In the data set davisdata Seat is a categorical variable, alcohol is numerical 

we try to predict alcohol ~Seat so we have to use the ....... helper file 

# Results  

## Descriptive results 

### Graphical Results 

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
 Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

This boxplot shows that.....


### Numerical Results 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
The numerical summary shows that....


### Inferential Results 

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
the p-value is 0.00116, less than 0.05 so we reject the null hypothesis. 
 There is a difference in alcohol onsumption based on where people sit 
 
## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```



## Conclusions







